\textbf{SPECFEM3D}\\ \textbf{User Manual}

### 2010-11-22 doc/USER_MANUAL/manual_SPECFEM3D.tex
changed "it's" to "it is" and "paper" to "article"

The next release of the code will include support for GPU graphics card acceleration \citep{KoMiEr09,KoErGoMi10,MiKo10,Kom11}
as well as Convolutional or Auxiliary Differential Equation Perfectly Matched absorbing Layers (C-PML or ADE-PML) \citep{KoMa07,MaKoEz08,MaKoGe08,MaKo09,MaKoGeBr10}.
The next release will use the PT-Scotch parallel library for mesh partitioning.

@@

Besides earthquake simulations, SPECFEM3D includes functionality for seismic noise tomography as well.
In order to proceed successfully in this chapter, it is critical that you have already familiarized yourself
with procedures for meshing (Chapter \ref{cha:Mesh-Generation}),
creating distributed databases (Chapter \ref{cha:Creating-Distributed-Databases}),
running earthquake simulations (Chapters \ref{cha:Running-the-Solver})
and adjoint simulations (Chapter \ref{cha:Adjoint-Simulations}).
Also, make sure you read the paper `Noise cross-correlation sensitivity kernels' \citep{trompetal2010},
in order to understand noise simulations from a theoretical perspective.

@@

Note that it's better to run the three steps continuously within the same job,
otherwise you have to collect the saved surface movies from the old nodes/CPUs to the new nodes/CPUs.
This process varies from cluster to cluster and thus cannot be discussed here.
Please ask your cluster administrator for information/configuration of the cluster you are using.\\

>>>>

The next release of the code will include support for GPU graphics card acceleration \citep{KoMiEr09,KoErGoMi10,MiKo10,Kom11}
as well as Convolutional or Auxiliary Differential Equation Perfectly Matched absorbing Layers (C-PML or ADE-PML) \citep{KoMa07,MaKoEz08,MaKoGe08,MaKo09,MaKoGeBr10}.
It will also use the PT-Scotch parallel library for mesh partitioning.

@@

Besides earthquake simulations, SPECFEM3D includes functionality for seismic noise tomography as well.
In order to proceed successfully in this chapter, it is critical that you have already familiarized yourself
with procedures for meshing (Chapter \ref{cha:Mesh-Generation}),
creating distributed databases (Chapter \ref{cha:Creating-Distributed-Databases}),
running earthquake simulations (Chapters \ref{cha:Running-the-Solver})
and adjoint simulations (Chapter \ref{cha:Adjoint-Simulations}).
Also, make sure you read the article `Noise cross-correlation sensitivity kernels' \citep{trompetal2010},
in order to understand noise simulations from a theoretical perspective.

@@

Note that it is better to run the three steps continuously within the same job,
otherwise you have to collect the saved surface movies from the old nodes/CPUs to the new nodes/CPUs.
This process varies from cluster to cluster and thus cannot be discussed here.
Please ask your cluster administrator for information/configuration of the cluster you are using.\\
